Hydrodynamics and rheology of an adhesive vesicle doublet

### 2019-02-08 vesicle_code/docs/adhesion/adhesion.tex
yny's edits Friday night

\begin{figure}[htp]
  \begin{minipage}{0.31\textwidth}
    \centering
    \includegraphics[height=5cm,trim={0cm 0cm 2cm 0cm},clip]{figs/adhesionPotential.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.31\textwidth}
    \centering
    \includegraphics[height=5cm]{figs/configCartoon.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.31\textwidth}
    \centering
    \includegraphics[height=5cm,trim={3cm 0cm 2cm 0cm},clip]{figs/Adhesion_Force.png}
  \end{minipage}
  \caption{\label{fig:adhesionModel} {\em Left}: The adhesion potential
  $\phi(z)$ in equation~\eqref{eq:adhesion_potential}.  Distances less
  than $\delta$ are repulsive and distances greater than $\delta$ are
  attractive.  {\em Center}: Each point on a vesicle is repelled or
  attracted by all points on the other vesicles.  {\em Right}: The
  resulting adhesive force is found by integrating over all points on
  all other vesicles (equation~\eqref{eqn:adhesionForce}).  The color is
  the dot product of the adhesion force with the vector joining the
  vesicles.  Therefore, the green and blue regions are repelled by the
  other vesicle while the yellow regions are attracted to the other
  vesicle.}
\end{figure}

@@

\begin{figure}[htp]
    \includegraphics[width=0.25\textwidth]{figs/angleDefinition.pdf}
    \includegraphics[width=0.25\textwidth]{figs/rotate1.pdf}
    \includegraphics[width=0.25\textwidth]{figs/rotate2.pdf}
   \caption{\label{fig:InclinationAngle} The definition of the
   inclination angle of a vesicle doublet at the center of an
   extensional flow.  An inclination angle of $\pi$ indicates a doublet
   whose long axis is parallel to the diverging direction, while an
   inclination angle of $\pi/2$ indicates a doublet whose short axis is
   parallel to the diverging direction.  The square mark is a stagnation
   point and the round point is located at the center of the vesicle.}
   \end{figure}

@@

In Figures~\ref{fig:extensional1},
snapshots of a fluid trap containing a vesicle doublet of reduced area
$\Delta A = 0.7$ are simulated at different extensional rates.  While
this doublet remains bound for all the
considered extensional rates, a doublet with a reduced area of $\Delta A
= 0.8$ is split with a critical extensional rate $\chi_c =0.1$
(bottom row in Figure~\ref{fig:extensional3}).  
%
\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}\\
   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
  \caption{\label{fig:extensional1} A doublet inside a fluid trap.  The
  reduced area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} =
  0.7$, the adhesion length scale is $\delta = 0.4$, and the extensional
  rate $\chi = 0.02$ ({\em top}) and $\chi=0.7$ ({\em bottom}).  The center of the vesicle, denoted with a
  black square, is a stagnation point.}
  \end{figure}
  %
  For extensional rates and reduced areas that result in a bound vesicle doublet, 
we observe that the doublet always rotate from $\theta=\pi/2$ configuration towards
the more stable $\theta=\pi$ configuration, as shown in Figures~\ref{fig:extensional1}--\ref{fig:extensional3}.
We also observe that in most cases with moderate extensional flow rates the doublet falls short of 
aligning their long axis with the diverging direction.

@@

 \begin{figure}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}\\
    \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
  The reduced area $\Delta A = 0.7$ ({\em top}) and $\Delta A=0.8$ ({\em bottom}). The Hamaker constant is $\mathcal{H} =
  0.7$, the adhesion length scale is $\delta = 0.4$, and the extensional
  rate $\chi = 0.1$.  The center of the vesicle, denoted with a black
  square, is a stagnation point.}
  \end{figure}

@@

Finally, to further characterize the rotating dynamics of a doublet in the fluid trap, we
compute and plot the vorticity and total force on a doublet with identical vesicles
with reduced area $\Delta A=0.7$, adhesion length $\delta = 0.4$, Hamaker constant $\mathcal{H} = 0.7$, and
extensional rate $\chi = 0.7$ in Figure~\ref{fig:extensionalVorticity}.
Starting from a doublet inclination angle $\theta=\pi/2$, 
the vesicle doublet slowly begins to rotate around $t\sim 265$
(see the left plot of
Figure~\ref{fig:extensionalInclinationAngle}).  We notice that the net force on each vesicle is almost 
anti-parallel to the diverging flow in the
far-field so to balance the hydrodynamic drag force that pulls the vesicles apart.

>>>>

\begin{figure}[htp]
  \begin{minipage}{0.31\textwidth}
    \centering
    \includegraphics[height=5cm,trim={0cm 0cm 2cm 0cm},clip]{figs/adhesionPotential.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.31\textwidth}
    \centering
    \includegraphics[height=5cm]{figs/configCartoon.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.31\textwidth}
    \centering
    \includegraphics[height=5cm,trim={3cm 0cm 2cm 0cm},clip]{figs/Adhesion_Force.png}
  \end{minipage}
  \caption{\label{fig:adhesionModel} {\em Left}: The adhesion potential
  $\phi(z)$ in equation~\eqref{eq:adhesion_potential}.  Distances less
  than $\delta$ are repulsive and distances greater than $\delta$ are
  attractive.  {\em Center}: Each point on a vesicle is repelled or
  attracted by all points on the other vesicles.  {\em Right}: The
  resulting adhesive force is found by integrating over all points on
  all other vesicles (equation~\eqref{eqn:adhesionForce}).  The color is
  the dot product of the adhesion force with the vector joining the
  vesicles.  Therefore, the green and yellow regions are repelled by the
  other vesicle while the blue regions are attracted to the other
  vesicle.}
\end{figure}

@@

\begin{figure}[htp]
    \includegraphics[width=0.25\textwidth]{figs/rotate1.pdf}
    \hspace{20pt}
    \includegraphics[width=0.25\textwidth]{figs/angleDefinition.pdf}
    \hspace{20pt}
    \includegraphics[width=0.25\textwidth]{figs/rotate2.pdf}
   \caption{\label{fig:InclinationAngle} The definition of the
   inclination angle of a vesicle doublet at the center of an
   extensional flow.  An inclination angle of $\pi$ indicates a doublet
   whose long axis is parallel to the diverging direction, while an
   inclination angle of $\pi/2$ indicates a doublet whose short axis is
   parallel to the diverging direction.  The square mark is a stagnation
   point and the round point is located at the center of the vesicle.}
   \end{figure}

@@

In Figures~\ref{fig:extensional1},
snapshots of a fluid trap containing a vesicle doublet of reduced area
$\Delta A = 0.7$ are simulated at different extensional rates.  While
this doublet remains bound for all the
considered extensional rates, a doublet with a reduced area of $\Delta A
= 0.8$ is split with a critical extensional rate $\chi_c =0.1$
(bottom row in Figure~\ref{fig:extensional3}).  
%
\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}\\
   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
  \caption{\label{fig:extensional1} A vesicle doublet in an extensional flow with an initial inclination angle $\theta=\pi/2$.  The
  reduced area $\Delta A = 0.7$, the Hamaker constant $\mathcal{H} =
  0.7$, the adhesion length scale $\delta = 0.4$, and the extensional
  rate $\chi = 0.02$ ({\em top}) and $\chi=0.7$ ({\em bottom}).  The center of the vesicle, denoted with a
  black square, is a stagnation point.}
  \end{figure}
  %
  For extensional rates and reduced areas that result in a bound vesicle doublet, 
we observe that the doublet always rotate from $\theta=\pi/2$ configuration towards
the more stable $\theta=\pi$ configuration, as shown in Figures~\ref{fig:extensional1}--\ref{fig:extensional3}.
We also observe that in most cases with moderate extensional flow rates the doublet falls short of 
aligning their long axis with the diverging direction.

@@

 \begin{figure}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}\\
    \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
  \caption{\label{fig:extensional3} A vesicle doublet in an extensional flow with an initial inclination angle $\theta=\pi/2$.
  The reduced area $\Delta A = 0.7$ ({\em top}) and $\Delta A=0.8$ ({\em bottom}). The Hamaker constant $\mathcal{H} =
  0.7$, the adhesion length scale $\delta = 0.4$, and the extensional
  rate $\chi = 0.1$.  The center of the vesicle, denoted with a black
  square, is a stagnation point.}
  \end{figure}

@@

Finally, to further characterize the rotating dynamics of a doublet in the fluid trap, we
compute and plot the vorticity and total force on a doublet with identical vesicles
with reduced area $\Delta A=0.7$, adhesion length $\delta = 0.4$, Hamaker constant $\mathcal{H} = 0.7$, and
extensional rate $\chi = 0.7$ in Figure~\ref{fig:extensionalVorticity}.
Starting from a vesicle doublet with an initial inclination angle $\theta=\pi/2$, 
the doublet slowly begins to rotate around $t\sim 265$
(see the left plot of
Figure~\ref{fig:extensionalVorticity}).  We notice that the net force on each vesicle is almost 
anti-parallel to the diverging flow in the
far-field so to balance the hydrodynamic drag force that pulls the vesicles apart.
